On Extensibility and Personalizability of Multi-Modal Trip Planning

### 2016-03-03 paper.tex
Added reference paper on scenic routing.

However, relatively limited effort has been devoted to designing and
implementing real-world multi-modal trip planners that captures user
constraints and preferences over the \tit{cost base}, possibly
extended from the user with auxiliary \tit{cost metrics},
such as crime rates and pollution statistics.

>>>>

However, relatively limited effort has been devoted to designing and
implementing real-world multi-modal trip planners that captures user
constraints and preferences over the \tit{cost base}, possibly
extended from the user with auxiliary \tit{cost metrics},
such as crime rates and pollution statistics.
One notable work by Nina et al.\cite{nina2016no} introduced
system \tit{Autobahn} for generating scenic routes using
Google Street View images to train a deep neural network
to classify route segments based on their visual features.
Although \tit{Autobahn} computes scenic routes using computer
vision techniques, it does not account for extensibility
and personalizability.
